\documentclass{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{titling}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{setspace}
\usepackage{mathtools}
\usepackage{helvet}
\usepackage[skip=10pt plus1pt, indent=40pt]{parskip}


\author{Guzmán Zugnoni}
\title{Non-integer order derivatives}

\renewcommand{\maketitle}{
\begin{center}
	\Huge\textbf \thetitle
\end{center}
}

\setlength{\parindent}{0pt}
%\setlength{\parskip}{20pt}
\doublespacing
\renewcommand{\familydefault}{\sfdefault}

\def\squad{\hskip2\fontdimen3\font}

\DeclareMathOperator{\di}{\,d\!}
\newcommand*\Eval[3]{\left[#1\right]_{#2}^{#3}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\newcommand{\IntSub}[1]{
{\textup{Substitution:}} \\
&\quad
\boxed{\begin{aligned}
		#1
\end{aligned}}
}


\begin{document}
\maketitle

\newpage

\tableofcontents

\newpage

\section{Introduction}

My interest in this topic was born when we learned about the notion of second
and higher order derivatives. We learnt that there was a meaning and an
application of taking a derivative multiple times. However, when learning about
second order derivatives, the notation used to represent this operation made
me relate it to another concept we had learnt about, exponents.

To represent the second derivative for instance, one writes $\frac{d^2}{dx^2}$,
which encodes the fact that $\frac{d}{dx}$ was written twice by ``multiplying''
them and writing a $2$ in the exponent. This made me think about
exponentiation, which is the process of repeated multiplication, where
similarly $x \cdot x = x^2$. However, for exponentiation, we learn that it is
possible to exponentiate to non-integral, and non-positive powers, such as
$x^{-1}=\frac{1}{x}$ or $x^\frac{1}{2} = \sqrt{x}$, which have meaning and are
useful in solving mathematical problems, and this led me to think about if
there existed a similar notion regarding derivatives.

My focus in this exploration is going to be to find a way to generalise
higher-order derivatives to all $\mathbb{R}$, and not only $\mathbb{Z}_{\geq0}$.

\section{Negative order derivatives}

The most natural order to start defining non-integral derivatives is the same
order in which non-integer exponents are first learned: exponentiating to
negative integers. The expression $\frac{d^{-1}}{dx^{-1}}$ has no obvious
meaning, but it can be interpreted like one interprets exponents

Firstly, throughout the exploration, I will use the notation
$$  \frac{d^\alpha}{dx^\alpha}=\
	D^\alpha \quad \forall \squad \alpha \in \mathbb{R}$$
And for an arbitrary $\alpha$-differentiable function $f$:
$$\frac{d^\alpha}{dx^\alpha}\left(f\right) = D^\alpha f$$

Now using this notation, by the definition of the second derivative, given an
arbitrary differentiable function $f$: $$D^1D^1 f = D^2 f$$ This can also be
extended for the notion of a third derivative: $$D^1D^2 f = D^3 f$$ It can be
extrapolated that, more generally,
\begin{equation}
	\label{der_sum}
	D^nD^m = D^{n+m} \quad \forall \squad n,m \in \mathbb{Z}^{+}
\end{equation}

This leads to defining negative order derivatives like negative order
exponents, where $x^1 \cdot x^{-1}= x^0$. Similarly, one might say that, by
(\ref{der_sum})
\begin{equation}
	\label{inv_eq}
	D^1D^{-1} f = D^0 f
\end{equation}
and this leads to having to define what $D^0$ means.

It makes sense intuitively that taking the derivative of a function 0 times
would leave it without change, but I will check this verifies
algebraically. This is easy to do, as $$D^1 D^0 f = D^{1+0} f = D^1 f$$
Removing the $D^1$ from both sides by taking their integrals gives the equation
$$D^0 f = f$$ which proves the intuition that this operation does nothing. This
means that the 0th power of the derivative operator is the identity operator.

Going back to (\ref{inv_eq}), we now see that
\begin{equation}
	\label{inv_eq_simplified}
	D^1D^{-1} f = f
\end{equation}
Since this is true for any arbitrary differentiable function $f$, and the order
of these two doesn't matter, i.e. $D^1D^{-1}=D^{-1}D^1$, we see these two
operators are inverses of each other, as composing them results in the
identity. Luckily, we know the inverse to the derivative operator, and that is
the integral. To find the value of $D^{-1}$, we can take the integral of both
sides of (\ref{inv_eq_simplified}), leading to
$$
D^{-1} f = \int f dx
$$

Which, when applying $D^{-1}$ n times, leads to the result
$$
D^{-n} f = \underbrace{\int \int \ldots \int}_\text{$n$ times}
		   f\left(t\right) \di t \qquad \forall n \in \mathbb{Z}
$$

So far, negative order derivatives seem simple, as they match an initial
intuition very cleanly: 0th derivatives do nothing, and negative derivatives do
the opposite to a derivative. While this matches the intuition, this might have
been wrong, and it is important to verify this formally

After learning about negative derivatives, one may see that they are hard to
evaluate, as a consequence of them involving integrals.

For instance, taking $f = \frac{8}{(x^2+1)^3}$:
$$
D^2\left(\frac{8}{(x^2+1)^3}\right) =
D\left(\frac{-48x}{(x^2+1)^4}\right) =
\frac{48x(7x^2-1)}{(x^2+1)^5}
$$

Despite there not being a general formula for the nth derivative of an
arbitrary function, one can easily arrive at the desired derivative by
performing repeated derivatives.

However, when trying to do the opposite, i.e. $D^{-2}$, the process is much
harder:

$$
D^{-2}\left(\frac{8}{(x^2+1)^3}\right) =
D^{-1}\left(\frac{x\left(3x^2+5\right)}{\left(x^2+1\right)^2} +
3\tan^{-1}{x} + C_1 \right)
$$

And performing the process of integration again will result in an even more
complicated result, with which performing repeated integration becomes
exponentially harder. Therefore, there is motivation to find a suitable
alternative to performing the integral every time, and a method to do this is
known as Cauchy's formula for repeated integration.

\section{Cauchy's formula for repeated integration}

The motivation for this formula is finding areas of threedimensional objects,
where integration may be performed twice to find the volume of an
object. However this formula may be used for the purposes of this investigation.

Cauchy's formula for repeated intregration is given thusly:
$$
\int_a^x
\int_a^{t_1}
\int_a^{t_2}
\ldots
\int_a^{t_{n-1}}f\left(t_n\right) dt_n \ldots dt_2 dt_1
=
\frac{1}{(n-1)!}\int_a^x\left(x-t\right)^{n-1}f\left(t\right)dt.
$$
where here $a$ is an arbitrary constant, alike the constant of integration.

This formula may be used to calculate the nth antiderivative for any function
performing a single integration. I will give a few examples of this method in
use, calculating them both by the normal method and Cauchy's Formula. For the
sake of ease, I will assume appropiate initial conditions such that all
constant of integration will be $0$.


\subsection{Proof for $n \in \mathbb{Z}$}

This may be proven for $n \in \mathbb{Z}^+$ by induction, for an arbitrary
integrable function $f$. The base case is n=1, where it should simply be equal
to
$\int
f\left(x\right)dx$:
$$
\frac{1}{(1-1)!}\int_a^x\left(x-t\right)^{1-1}f\left(t\right)dt =
\frac{1}{(0)!}\int_a^x\left(x-t\right)^{0}f\left(t\right)dt =
\int_a^xf\left(t\right)dt
$$
The last integral is the same as the indefinite integral, as it evaluates to
the antiderivative at $x$, $F(x)$, plus a constant $C$, which in this case is
$-f(a)$, which means that the base case is true.

Thus, let $P_n$ be the proposition that Cauchy's formula holds for $n$. We may
assume that $P_k$ holds for some $k \in \mathbb{Z}^+$, and prove $P_{k+1}$
holds.

The formula for $n = k + 1$ would be:
$$
\int_a^x
\boxed{
\int_a^{t_1}
\int_a^{t_2}
\ldots
\int_a^{t_{k-1}}
\int_a^{t_k}f\left(t_{k+1}\right) \di t_{k+1}\di t_k\di t_{k-1} \ldots \di t_2}\di t_1
$$
The boxed region contains $k$ integrals, and thus, since $P_k$ holds, we may apply
Cauchy's formula to the integrals, which would result in the expression:
$$
\int_a^x
\frac{1}{(k-1)!}\int_a^{t_1}\left(t_1-t\right)^{k-1}f\left(t\right)\di t\di t_1
$$

Since when substituting $k+1$ in the formula the $x-t$ expression is raised to
the $k$th power, it is a good idea to achieve this. To do this, we must raise
the current power by 1, which may be achievable by writing it as a derivative,
like so:
$$
\int_a^x
\frac{1}{(k-1)!}\int_a^{t_1}\frac{\di}{\di t_1}\left[\frac{1}{n}\left(t_1-t\right)^k f\left(t\right)\right]\di t\di t_1
$$
The $f(t)$ term is included in the derivative, as it is a constant in terms of
$t_1$. This expression is very similar to the Fundamental Theorem of Calculus,
which states:
\begin{equation}
	\label{fundamental_theorem_of_calculus}
\frac{\di}{\di x}\int_a^bf(x)\di x = \int_a^b\frac{\di}{\di x}f(x) \di x = f(b)- f(a)
\end{equation}
Applying (\ref{fundamental_theorem_of_calculus}) results in the expression becoming
\begin{gather*}
\int_a^x
\frac{1}{(k-1)!}\frac{\di}{\di t_1}\left[\int_a^{t_1}\frac{1}{n}\left(t_1-t\right)^k f(t)\di t\right]\di t_1 \\
\int_a^x
\frac{\di}{\di t_1}\left[\frac{1}{(k-1)!}\int_a^{t_1}\frac{1}{n}\left(t_1-t\right)^k f(t)\di t\right]\di t_1 \\
\int_a^x
\frac{\di}{\di t_1}\left[\frac{1}{(k-1)!}\frac{1}{n}\int_a^{t_1}\left(t_1-t\right)^k f(t)\di t\right]\di t_1 \\
\int_a^x
\frac{\di}{\di t_1}\left[\frac{1}{k!}\int_a^{t_1}\left(t_1-t\right)^k f(t)\di t\right]\di t_1
\end{gather*}
Applying(\ref{fundamental_theorem_of_calculus}) again eliminates the outer integral,
and results in
$$
\frac{1}{k!}\int_a^x\left(x-t\right)^k f(t)\di t -
\frac{1}{k!}\int_a^a\left(a-t\right)^k f(t)\di t =
\frac{1}{k!}\int_a^x\left(t_1-t\right)^k f(t)\di t
$$
which is $P_{k+1}$, and therefore by the principle of mathematical induction,
$$
\left(\left(P_k \implies P_{k+1}\right) \land P_1\right)
\implies P_n \forall n \in \mathbb{Z}^+
\qquad \blacksquare
$$

\subsection{Example}
As an example of how to use this formula, I will calculate a simple antiderivative,
that of $x^2$. Firstly, using the simple method of integration.
\begin{flalign*}
	\iiiint x^2 \di x\di x\di x\di x
	&=\iiint \frac{x^3}{3} \di x\di x\di x \\
	&=\iint \frac{x^4}{12}\di x\di x \\
	&=\int \frac{x^5}{60} \di x \\
	&=\frac{x^6}{360}
\end{flalign*}
And secondly, using Cauchy's formula for integration:
\begin{flalign*}
	\frac{1}{(4-1)!}\int_0^x \left(x-t\right)^{4-1}	t^2 \di t
	=&\frac{1}{3!}\int_0^x \left(x-t\right)^3 t^2 \di t\\
	=&\frac{1}{6}\int_0^x \left(x^3 - 3x^2t + 3xt^2 - t^3\right)t^2 \di t \\
	=&\frac{1}{6}\int_0^x x^3t^2 - 3x^2t^3 + 3xt^4 - t^5 \di t \\
	=&\frac{1}{6} \Eval{\frac{x^3t^3}{3} - \frac{3x^2t^4}{4} + \frac{3xt^5}{5} - \frac{t^6}{6}}{0}{x} \\
	=&\frac{1}{6} \left(\frac{1}{3}x^6 - \frac{3}{4} x^6 + \frac{3}{5} x^6 - \frac{1}{6}x^6 \right) \\
	=&\frac{1}{6} \left(\frac{x^6}{60} \right) \\
	=&\frac{x^6}{360}
\end{flalign*}

The results are the same and thus the formula seems to hold for a simple
function. However, one may realise that the second solution is in fact longer
and more complex than the traditional way of evaluating the integral. This is
much more evident, for instance in the example of $D^{-3} \sin{x}$, where
$\iiint \sin{x} \di x$ is rather easy to evaluate because of the simplicity and
cyclical nature of its antiderivatives, whereas $\frac{1}{2}\int
\left(x-t\right)^2 \sin t\di t$ involves much more work and complex
techniques. This is a result of the fact that integrals tend to become more
complex to evaluate when more terms are introduced. Thus, despite the fact that
this compresseses the work needed to be done to one integral, the complexity is
much greater.

This means that Cauchy's formula is in fact, not a practical way to calculate
negative order derivatives in most situations, even though it seems like it
would be. Cauchy's formula however has other uses cases, in places like applied
mathematics for calculating integrals numerically in multi-variable calculus
for instance, which are outside the scope of this exploration, but most
importantly for this exploration, this formula can be generalised for
non-integer integrals.

\subsection{Generalising Cauchy's integral formula for $x \in \mathbb{R}$}

Now that an easy way to perform the inverse of a derivative has been
established, it is reasonable to assume that this might make it possible to
extend this operation to all reals.

This is true, as it is possible, however, a slight consideration must be made.
The formula for repeated integration is thus

$$
D^{-n}f(x) = \frac{1}{(n-1)!}\int_a^{x}\left(x-t\right)^{n-1}f(t)\di t
$$

However, if one tries to substitute something that is not a positive integer
for n, one comes across the problem of having to evaluate
$\frac{1}{(n-1)!}$. Generalising factorials to all $\mathbb{R}$ is complex,
involving techniques in real analysis. However, since this is not the focus of
this exploration, I will use the result without proving it. This generalisation
is named $\Gamma(x)$, and its formula is given as
$$
\Gamma(x)=\int_0^{\infty} e^{-t}t^{x-1}dt = (x-1)!
$$
Having this function, we can thus express the formula for repeated integration as
$$
D^{-\alpha}f(x) = \frac{1}{\Gamma\left(\alpha\right)}\int_a^{x}\left(x-t\right)^{\alpha-1} f(t)\di t
$$

Having this, we can now define fractional calculus and its main operator,
the differintegral.


\section{Fractional calculus}
\subsection{The differintegral operator}
Having defined a way to take integrals a non-integral number of times, we can
now define an operator that can ``take the derivative $x$ times'', where
$x$ could be any real number

This could be first approached by saying that, to take $D^2$ for instance, we
may take $D^{-\left(-2\right)}$ and evaluate using Cauchy's formula. However,
this does not work, as when trying to evaluate $\Gamma(-1)$, we find that it is
not defined. This is true for all negative integers, and thus we must define an
operator that can properly take these derivatives.

To do this, it is useful to split all numbers into their integer and
non-integral parts. To start with, we consider a positive number $x \in
\mathbb{R}$, which we split into its integer and its fractional part: $x = n +
\alpha, \quad n \in \mathbb{Z}^+, \squad 0 \leq \alpha < 1$, which is the
decomposition of the number as its integer and real part. Therefore, we could
write $D^x=D^nD^\alpha$, by the property discussed in the previous
section. This is very useul because $D^n$ is simply the nth derivative, which
is simply defined as the repetition of derivatives, and additionally $D^\alpha$
can be calculated using Cauchy's formula, and therefore we reach the result:

\begin{align*}
	D^x f   &= \frac{d^n}{dx^n} D^\alpha f \\
			&= \frac{d^n}{dx^n} \frac{1}{\Gamma\left(\alpha\right)}
			 \int_a^x (x-t)^{\alpha-1} f(t) \di t
\end{align*}

This same working may also be used for negative numbers: $x = n + \alpha \quad
\alpha,n < 0$, using either Cauchy's Formula or a manual method to compute the
integral $n$ times.

\begin{align*}
	D^x f   &= D^{-n} D^\alpha f \\
			&= \frac{1}{(n-1)!} \int_a^x (x-t)^{n-1}
			 \left(\frac{1}{\Gamma\left(\alpha\right)}
			 \int_0^t (t-\omega)^{\alpha - 1} f(\omega) \di \omega\right)\di t
\end{align*}

This may be condensed into a single operator, for both negative and positive
numbers:
\begin{equation*}
	D^\alpha f(x) =
	\begin{cases}
		\frac{d^n}{dx^n} D^{\alpha - n} f(x)
		& \text{if } \alpha \geq 1, \text{where } n = \floor{\alpha}\\

		I^{-n}D^{\alpha - n} f(x)
		& \text{if } \alpha \leq -1, \text{where } n = \ceil{\alpha} \\

		\frac{d}{dt} \frac{1}{\Gamma\left(\alpha\right)} \int_a^x (x-t)^{\alpha-1} f(t) \di t
		& \text{if } 0 < \alpha < 1 \\

		\frac{1}{\Gamma\left(\alpha\right)} \int_a^x (x-t)^{\alpha-1} f(t) \di t
		& \text{if } -1 < \alpha < 0 \\

		f(x) & \text{if } \alpha = 0
	\end{cases}
\end{equation*}

Where $I^n$ represents the $n$-th integral, which as discussed previously may
be calculated using several methods, like Cauchy's method or manually. The
above method of defining fractional integrals is known as the Riemann-Liouville
integral. (should I cite this?)

For instance,
$$
D^{\frac{11}{4}} f = D^{2+\frac{3}{4}}
				 = \frac{d^2}{dx^2}\frac{1}{\Gamma\left(\frac{3}{4}\right)}
				 \frac{d}{dx} \int_a^x\left(x-t\right)^{-\frac{1}{4}} f(t) \di t
$$

and

$$
D^{-\frac{13}{3}} f = D^{-4-\frac{1}{3}}
					= I^4 \frac{1}{\Gamma\left(-\frac{1}{3}\right)} \int_a^x \left(x-t\right)^{-\frac{4}{3}} f(t) \di t
$$

This provides an easy and algorithmic way to calculate the $\alpha$ derivative
of a function, leaving only the inner integral to calculate, which depends on
the function. In the following section, some example derivatives will be
calculated.

\subsection{Examples}

To begin with, I will calculate the most simple fraction for the derivative
power, the $\frac{1}{2}$ power, as this is ``the first'' fraction, as it is the
first fraction of the form $\frac{1}{n}$ that is not an integer, and the
function $x^2$, as integer derivatives of polynomials are simple.

$$
D^{\frac{1}{2}} \left(x^n\right) = \frac{d}{dx} \frac{1}{\Gamma\left(\frac{1}{2}\right)} \int_a^x \left(x-t\right)^{-\frac{1}{2}} t^2 \di t
$$

For this purpose, $\Gamma\left(-\frac{1}{2}\right)$ needs to be known, and this
value is a special value of the gamma function, whose calculation is outside
out of the scope of this investigation, but nevertheless gives
$\Gamma\left(\frac{1}{2}\right) = \sqrt{\pi}$.

\begin{flalign*}
	&\frac{d}{dx} \frac{1}{\sqrt{\pi}} \int_a^x \frac{t^2}{\left(x-t\right)^{\frac{1}{2}}} \di t \\
	&\IntSub{
		\text{let } u&=x-t \\
			du&=-dt \\
			t \to a &\implies u \to x-a \\
			t \to x &\implies u \to 0
	} \\
	&=\frac{d}{dx}\frac{-1}{\sqrt{\pi}} \int_{x-a}^0 \frac{\left(x-u\right)^2}{u^{\frac{1}{2}}} \di u && \\
	&= \frac{d}{dx}\frac{-1}{\sqrt{\pi}} \int_{x-a}^0 \frac{x^2-2xu+u^2}{u^{\frac{1}{2}}} \di u && \\
	&= \frac{d}{dx}\frac{1}{\sqrt{\pi}} \int_0^{x-a} x^2u^{-\frac{1}{2}}-2xu^{\frac{1}{2}}+u^{\frac{3}{2}} \di u && \\
	&= \frac{d}{dx}\frac{1}{\sqrt{\pi}} \Eval{2x^2u^{\frac{1}{2}}-\frac{4}{3}xu^{\frac{3}{2}}+\frac{2}{5}u^{\frac{5}{2}}}{u=0}{u=x-a} && \\
	&= \frac{d}{dx}\frac{1}{\sqrt{\pi}} \left(2x^2\left(x-a\right)^{\frac{1}{2}}-\frac{4}{3}x\left(x-a\right)^{\frac{3}{2}}+\frac{2}{5}\left(x-a\right)^{\frac{5}{2}}\right) && \\
	&= \frac{1}{\sqrt{\pi}} \left(4x\left(x-a\right)^{\frac{1}{2}} +
								  \frac{x^2}{\left(x-a\right)^{\frac{1}{2}}} -
								  \frac{4}{3}\left(x-a\right)^{\frac{3}{2}} -
								  2x\left(x-a\right)^{\frac{1}{2}} +
\left(x-a\right)^{\frac{3}{2}}\right) && \\
									  &&
\end{flalign*}

This answer, in contrast to the usual derivative of $x^2$, this answer is
complex, and involves the constant $\frac{1}{\sqrt{\pi}}$. However, one of the
reasons for this complexity is the generic parameter $a$, which represents a
``starting point'' for the integration. Assigning it the value $a=0$ yields the following, much
simpler answer
\begin{align*}
	&\frac{1}{\sqrt{\pi}} \Eval{\left(4x\left(x-a\right)^\frac{1}{2} +
							   \frac{x^2}{\left(x-a\right)^\frac{1}{2}} -
							   \frac{4}{3}\left(x-a\right)^\frac{3}{2} -
							   2x\left(x-a\right)^\frac{1}{2} +
						       \left(x-a\right)^\frac{3}{2}\right)}
							   {a=0}{s}\\
	&=\frac{1}{\sqrt{\pi}} \left(4x\cdot\left(x\right)^\frac{1}{2} +
							   \frac{x^2}{x^\frac{1}{2}} -
							   \frac{4}{3}x^\frac{3}{2} -
							   2x \cdot x^\frac{1}{2} +
						       x^\frac{3}{2}\right) \\
	&=\frac{1}{\sqrt{\pi}} \left(4x^\frac{3}{2} +
								 x^\frac{3}{2}-
							     \frac{4}{3}x^{\frac{3}{2}} -
								 2x^\frac{3}{2} +
						         x^\frac{3}{2}\right) \\
	&=\frac{8}{3\sqrt{\pi}} x^\frac{3}{2}
\end{align*}

This is therefore, one of the possible half derivatives of $x^2$, as it
corresponds to one possible value of $a$. Moreover, because of the derivative rules
discussed above, it should be true that $D^\frac{1}{2}\frac{8}{3\sqrt{\pi}} x^\frac{3}{2} = 2x$,
as $D^\frac{1}{2}D^\frac{1}{2}x^2=D^{\frac{1}{2} + \frac{1}{2}} x^2=D x^2 = 2x$

Therefore, using the same method as above, we calculate the next half derivative.
\begin{align*}
	\frac{d}{dx}&D^\frac{1}{2} \frac{8}{3\sqrt{\pi}} x^\frac{3}{2} \\
	=&\frac{d}{dx}\frac{1}{\sqrt{\pi}} \frac{8}{3\sqrt{\pi}} \int_0^x \left(x-t\right)^{-\frac{1}{2}} t^\frac{3}{2} \di t \\
	=&\frac{d}{dx}\frac{8}{3\pi} \int_0^x \frac{t^\frac{3}{2}}{\left(x-t\right)^\frac{1}{2}} \di t \\
	 &\IntSub{
		 \text{let } u &= \sqrt{t} \\
		\di u &= \frac{1}{2\sqrt{t}} \di t = \frac{1}{2u} \di t \\
		2u \di u &= \di t \\
		t \to 0 &\implies u \to 0 \\
		t \to x &\implies u \to x
	} \\
	=&\frac{d}{dx}\frac{8}{3\pi} \int_0^{\sqrt{x}} \frac{u^3 \cdot 2u}{\sqrt{x-u^2}} \di u \\
	=&\frac{d}{dx}\frac{16}{3\pi} \int_0^{\sqrt{x}} \frac{u^4}{\sqrt{x-u^2}} \di u \\
\end{align*}

Because of the square root in the denominator, with a $x-u^2$, we should use a trigonometric
substitution to solve this, as such:
\begin{align*}
	 &\IntSub{
		 \text{let } u &= \sqrt{x}\sin{w} \\
		 \di u &= \sqrt{x}\cos{w} \di w \\
		 u \to 0 &\implies w \to 0 \\
		 u \to \sqrt{x} &\implies w \to \frac{\pi}{2} \\
	 } \\
	=&\frac{d}{dx}\frac{16}{3\pi} \int_0^{\frac{\pi}{2}} \frac{x^2\sin^4w\cdot \sqrt{x}\cos{w}}{\sqrt{x\left(1-\sin^2w\right)}} \di w \\
	=&\frac{d}{dx}\frac{16}{3\pi} \int_0^{\frac{\pi}{2}} \frac{x^2\sin^4w\cdot \sqrt{x}\cos{w}}{\sqrt{x}\cos w} \di w \\
	=&\frac{d}{dx}\frac{16x^2}{3\pi} \int_0^{\frac{\pi}{2}} \sin^4w \di w \\
	=&\frac{32x}{3\pi} \int_0^{\frac{\pi}{2}} \sin^4w \di w \\
\end{align*}

Because of how the integral is independent of the value of $x$, we can take the
$x$ term out, and evaluate the integral on its own. The value of this integral
is calculable using some substitutions, but the calculation of this integral is
outside of the scope of this investigation. Therefore, the value of this
integral will be taken as a given and not proven. The value of this integral is
$\frac{3\pi}{16}$, and therefore we may calculate the previous derivative.

\begin{align*}
	&\frac{32x}{3\pi} \int_0^{\frac{\pi}{2}} \sin^4w \di w \\
	=&\frac{32x}{3\pi} \frac{3\pi}{16} \\
	=&\frac{32x\cdot3\pi}{16\cdot 3\pi} \\
	=&2x
\end{align*}
The result is what is expected, as applying the half derivative twice resulted
in the same output as the original derivative

\subsection{Properties of fractional derivatives}
\subsection{Graphical interpretations of fractional derivatives}
\subsubsection{Non-locality}

\end{document}
